---
title: "Assignment One"
output: html_notebook
---
<br>
Set up the working directory for this assignment.
```{r}
setwd("/Users/rodneydavermann/Documents/Fall2021/R_Statistics /Assignments/RStatistics_AssignmentOne")
getwd()
```
<br>
1) Write code that allows you to create a vector x with the numbers {10,20,30,100,150,10,30,50}. Then, insert the number 168 between the third and fourth elements and assign the result of this insertion to x again.
```{r}
# Create the x vector
x <-c(10,20,30,100,150,10,30,50)
x
```
<br>
Insert the number 168 between the third which is 30 and fourth elements that is 100.
```{r}
# x vector
x <-c(10,20,30,100,150,10,30,50)
# We are using the append function to insert 168. 
x <-append(x,168,3)
x
```
<br>
2) Create a data frame with the following four columns: x (from the previous question), x1, x2, and y. Name the data frame DFAsg1

```{r}
# Create x1, x2, vectors
x1 <-round(rnorm(9,5,1),1)
x2 <-round(rnorm(9,5,1),1)
# Use sort and rep functions to create y vector
y <-sort(rep(c("A","B","C"),3), decreasing = F)
y
x1
x2
```
```{r}
# create the dataframe DFAsg1
DFAsg1 <-data.frame(x,x1,x2,y)
DFAsg1
```
<br>
3) Use the data frame DFAsg1 as a reference. Write ONE LINE of code that returns the standard deviation of the values of x for each of the letters A, B, and C.
```{r}
# use tapply and round functions to returns the sd of x column with three significative digits. 
StandardDeviation<-round(tapply(DFAsg1$x,DFAsg1$y,sd),3)
StandardDeviation
```
<br>
4)Use the data frame DFAsg1 as a reference. 
Write ONE LINE of code that returns the average of x1 and x2.
```{r}
# Using apply function to calculate the mean of x1 and x2, and round the results to three digits.  
Average_x1_x2<-round(apply(DFAsg1[,c(-1,-4)],2,mean),3)
Average_x1_x2
```
<br>
5) Use the data frame DFAsg1 as a reference. Write ONE LINE of code that returns the values of x2 for records (rows) where the letter is B or C (i.e., return the values of x2 excluding rows where the letter is A)
```{r}
# using subset function to retrieve x2 value where y is B or C
new_x2 <-subset(DFAsg1, select = c(x2,y), subset = (y=="B" | y=="C"))
new_x2
```






